---
title: "mrgsim.sa: sensitivity analysis with mrgsolve"
output: github_document
---


A simple, clean workflow for sensitivity analysis with mrgsolve. 
<hr>
<BR>

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = ".",
  fig.path = "man/figures/README-", 
  fig.width = 8.5, 
  fig.align = "center"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

```{r, message = FALSE, warning = FALSE}
library(mrgsim.sa)
```

Models in mrgsolve have "parameters" associated with them. 

```{r}
#| message: false
mod <- modlib("pk1", end = 48, delta = 0.1)

param(mod)
```

Parameters are name-value pairs that are usually involved in controlling how 
the system advances in time. Parameters could be clearances (`CL`), rate 
constants (`k`), pharmacodynamic parameters (`EC50`) or even covariates 
(`WT` ... weight). mrgsim.sa does one-at-a-time sensitivity analysis on 
parameters in your model.

## PK model sensitivity analysis by factor

The nominal (in model) parameter value is divided and multiplied by a factor,
generating minimum and maximum bounds for simulating a sequence of parameter
values. In this example, we vary `CL` and `V`, each one at a time.

```{r}
#| fig.height: 4
out <- 
  mod %>% 
  ev(amt = 100) %>% 
  select_par(CL, V) %>% 
  parseq_fct(.n = 5) %>% 
  sens_each() 

sens_plot(out, "CP")
```

In this sensitivity analysis, `CL` is varied at the value of `V` in the 
model parameter list and `V` is varied at the value of `CL` in the model 
parameter list. The black dashed line indicates the model prediction based on 
`CL` and `V` both as they are in the parameter list; this is the "reference".

The simulated data is returned in a long format
```{r}
out
```

The previous plot focused on relative changes in the PK profile for "lower" and 
"higher" values of `CL` and `V` according to the `parseq_` method. You can plot 
with a more quantitative color scale and legend using `grid = TRUE`.

```{r}
#| fig.height: 4
sens_plot(out, "CP", grid = TRUE)
```



## HIV viral dynamic model

In another example, we look at latent infected cell pool development over ten
years at different "burst" size, or the number of HIV particles released when
one cell lyses.


```{r}
#| message: false
#| fig.height: 5
#| fig.width: 7
mod <- mread("hiv", "inst/example")

mod %>% 
  update(end = 365*10) %>%
  parseq_range(N = c(900,1500), .n = 10) %>%
  sens_each(tscale = 1/365) %>% 
  sens_plot("L", grid = TRUE)
```


## Sensitivity analysis on custom sequences

The model is rifampicin PBPK.

```{r}
#| fig.height: 4
mod <- mread("inst/example/rifampicin.cpp", delta = 0.1)

sims <- 
  mod %>% 
  ev(amt = 600) %>% 
  parseq_manual(
    SFKp = seq_fct(.$SFKp, n = 20), 
    Kp_muscle = seq_even(0.001, 0.1, n = 6)
  ) %>% sens_each() 

sens_plot(sims, "Ccentral")
```

# Simulate a grid

To this point, we have always used `sens_each()` so that each value for each
parameter is simulated one at a time. Now, simulate the grid or all
combinations of the sensitivity parameters.

We use `parseq_cv()` here, which generates lower and upper bounds for the range
using 50% coefficient of variation.

```{r, fig.height = 7}

out <- 
  mod %>% 
  update(outvars = "Ccentral") %>%
  ev(amt = 600) %>% 
  parseq_cv(fBCLint_all_kg, .n = 5) %>% 
  parseq_cv(SFKp, Kp_muscle, .n = 3) %>% 
  sens_grid(recsort = 3) 

out

sens_plot(out, "Ccentral")
```

The output is more complicated because all the selected parameters have varying
"sensitivity" values. 

# Local sensitivity analysis

In local sensitivity analysis, we vary each sensitivity parameter a very small
amount around the parameter list (model) value and see how much the output 
changes for a unit change in the parameter. The "sensitivity" is plotted over
time. 

```{r}
#| fig.height: 5
#| fig.width: 7
#| message: false
mod <- modlib("pk2", delta = 0.1, end = 48)

doses <- ev(amt = 100)

out <- lsa(mod, var = "CP", par = "CL,V2,Q,V3", events = doses)

out

lsa_plot(out)
```

